Progress Report on the ``Adult Database'' Analysis

### 2009-11-12 report/paper.tex
adding more references.

To build a set of association rules we used the apriori algorithm that is featured
in the R arules package. Before running the algorithm we made some data preprocessing
for continuous attributes that are needed to build better and more general rules.

@@

\begin{thebibliography}{1}
\bibitem{1}
Mitchel, T.; Machine Learning; McGraw-Hill, 1997
\bibitem{2}
Han, J., Kamber, M., Pei, J.; Data Mining: Concepts and Techniques, Second Edition; Morgan Kaufmann, 2005
\bibitem{3}
H. Witten, I., Frank, E.; Data Mining: Practical Machine Learning Tools and Techniques, Second Edition; Morgan Kaufmann, 2005
\bibitem{4}
RapidMiner; \url{http://www.rapidminer.com/}, November 2009
\bibitem{5}
Ross Quinlan, J.; C4.5: Programs for Machine Learning; Morgan Kaufmann, 1992
\end{thebibliography}

@@

\begin{figure}
\centering
\includegraphics[width=10cm]{boxplot_hours_per_week.png}
\caption{Boxplot of the hours per week variable}
\label{fig:box_hours}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=10cm]{plot_plus_50_age.png}
\caption{Boxplot of the individuals' age, for each class of gain}
\label{fig:age_plus50}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=10cm]{plot_plus_50_education_num.png}
\caption{Boxplot of the individuals' education level, for each class of gain}
\label{fig:education_plus50}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=10cm]{plot_plus_50_hpw.png}
\caption{Boxplot of the individuals' hours of work per week, for each class of 
gain}
\label{fig:hpw_plus50}
\end{figure}

>>>>

To build a set of association rules we used the apriori algorithm that is featured
in the R \cite{6} arules \cite{7} package. Before running the algorithm we made some data preprocessing
for continuous attributes that are needed to build better and more general rules.

@@

\begin{thebibliography}{1}
\bibitem{1}
Mitchel, T.; Machine Learning; McGraw-Hill, 1997
\bibitem{2}
Han, J., Kamber, M., Pei, J.; Data Mining: Concepts and Techniques, Second Edition; Morgan Kaufmann, 2005
\bibitem{3}
H. Witten, I., Frank, E.; Data Mining: Practical Machine Learning Tools and Techniques, Second Edition; Morgan Kaufmann, 2005
\bibitem{4}
RapidMiner; \url{http://www.rapidminer.com/}, November 2009
\bibitem{5}
Ross Quinlan, J.; C4.5: Programs for Machine Learning; Morgan Kaufmann, 1992
\bibitem{6}
The R Project for Statistical Computing; http://www.r-project.org/, November 2009
\bibitem{7}
Hahsler, M., Gruen, B.; Hornik, K.; arules -- A Computational Environment for Mining Association Rules and Frequent Item Sets; Journal of Statistical Software 14/15, 2005
\end{thebibliography}

@@

\begin{figure}
\centering
\includegraphics[width=9cm]{boxplot_hours_per_week.png}
\caption{Boxplot of the hours per week variable}
\label{fig:box_hours}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=8cm]{plot_plus_50_age.png}
\caption{Boxplot of the individuals' age, for each class of gain}
\label{fig:age_plus50}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=9cm]{plot_plus_50_education_num.png}
\caption{Boxplot of the individuals' education level, for each class of gain}
\label{fig:education_plus50}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=9cm]{plot_plus_50_hpw.png}
\caption{Boxplot of the individuals' hours of work per week, for each class of 
gain}
\label{fig:hpw_plus50}
\end{figure}
